\bf Range Analysis for the IonMonkey JavaScript engine

### 2012-05-02 project-writings/paper.tex
fix ordering
typo

\section{Evaluation}
To evaluate our work, we tested for correctness using Mozilla's large
repository of regression tests, and measured the impact of our
optimization by the commonly available benchmark suites.
%% TODO : elim stats too

@@

We ran each benchmark suite on IonMonkey, both with and without our range
analysis pass, and measured the performance differences. The results are
summarized in Figures \ref{fig:v8bench}, \ref{fig:sunspider}, and
\ref{fig:kraken}. These figures were gathered using the SunSpider test harness,
which gives both a mean and a 95\% confidence interval\cite{sunspider}. Each
test was run 30 times.
\begin{figure}[H]
\begin{center}
\begin{tabular}{|l|l|l|l|l|}
\hline
    \textbf{Test}     &\textbf{Comparison} & \textbf{From}        & \textbf{To}           &  \textbf{Details} \\
\hline\hline
    Total:            &   -                & 3414.7ms $\pm$ 0.5\% &  3397.4ms $\pm$ 0.2\% & \\
\hline
\hline  crypto:       &   -                &  104.8ms $\pm$ 0.7\% &   104.7ms $\pm$ 0.4\% & \\
\hline  deltablue:    &   -                &  206.7ms $\pm$ 0.4\% &   205.8ms $\pm$ 0.4\% & \\
\hline  earley-boyer: &   1.009x as fast   & 1817.8ms $\pm$ 0.8\% &  1801.5ms $\pm$ 0.3\% &     significant \\
\hline  raytrace:     &   -                &  585.9ms $\pm$ 0.5\% &   584.8ms $\pm$ 0.3\% & \\
\hline  regexp:       &   -                &  492.9ms $\pm$ 0.6\% &   491.7ms $\pm$ 0.1\% & \\
\hline  richards:     &   1.018x as slow   &  149.0ms $\pm$ 0.7\% &   151.7ms $\pm$ 0.3\% &     significant \\
\hline  splay:        &   -                &   57.5ms $\pm$ 0.8\% &    57.1ms $\pm$ 0.6\% & \\
\hline
\end{tabular}
\caption{v8bench benchmark results}
\label{fig:v8bench}
\end{center}
\end{figure}

@@

To summarize our evaluation, we discovered the checks we eliminate do result in
some measurable performance increase. In extremly short-running tests such
SunSpider (see Figure \ref{fig:sunspider}), the additional compile-time
overhead that our pass requires yields slightly slower performance.

>>>>

\section{Evaluation}
To evaluate our work, we tested for correctness using Mozilla's large
repository of regression tests, and measured the impact of our
optimization by the commonly available benchmark suites.

@@

We ran each benchmark suite on IonMonkey, both with and without our
range analysis pass, and measured the performance differences. The
results are summarized in Figures \ref{fig:v8bench}, \ref{fig:kraken},
and \ref{fig:sunspider}. These figures were gathered using the
SunSpider test harness, which gives both a mean and a 95\% confidence
interval\cite{sunspider}. Each test was run 30 times.
\begin{figure}[H]
\begin{center}
\begin{tabular}{|l|l|l|l|l|}
\hline
    \textbf{Test}     &\textbf{Comparison} & \textbf{From}        & \textbf{To}           &  \textbf{Details} \\
\hline\hline
    Total:            &   -                & 3414.7ms $\pm$ 0.5\% &  3397.4ms $\pm$ 0.2\% & \\
\hline
\hline  crypto:       &   -                &  104.8ms $\pm$ 0.7\% &   104.7ms $\pm$ 0.4\% & \\
\hline  deltablue:    &   -                &  206.7ms $\pm$ 0.4\% &   205.8ms $\pm$ 0.4\% & \\
\hline  earley-boyer: &   1.009x as fast   & 1817.8ms $\pm$ 0.8\% &  1801.5ms $\pm$ 0.3\% &     significant \\
\hline  raytrace:     &   -                &  585.9ms $\pm$ 0.5\% &   584.8ms $\pm$ 0.3\% & \\
\hline  regexp:       &   -                &  492.9ms $\pm$ 0.6\% &   491.7ms $\pm$ 0.1\% & \\
\hline  richards:     &   1.018x as slow   &  149.0ms $\pm$ 0.7\% &   151.7ms $\pm$ 0.3\% &     significant \\
\hline  splay:        &   -                &   57.5ms $\pm$ 0.8\% &    57.1ms $\pm$ 0.6\% & \\
\hline
\end{tabular}
\caption{v8bench benchmark results}
\label{fig:v8bench}
\end{center}
\end{figure}

@@

To summarize our evaluation, we discovered the checks we eliminate do result in
some measurable performance increase. In extremly short-running tests such as
SunSpider (see Figure \ref{fig:sunspider}), the additional compile-time
overhead that our pass requires yields slightly slower performance.
